---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# diagnoser

<!-- badges: start -->
<!-- badges: end -->

The goal of diagnoser is to make it easy to diagnose regression models, `lm`, `lme`, or `lmer`.

## Installation

You can install the development version of diagnoser from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("i-kiwamu/diagnoser")
```

## Example 1: lm

First of all, make an object of diagnosis.

```{r example1}
library(ggplot2)
library(diagnoser)

# lm for mtcars
lm_mtcars <- lm(mpg ~ disp + hp + wt, mtcars)
diag_lm_mtcars <- diagnose(lm_mtcars)
```

### Measured vs fitted plot

```{r mf1}
plot(diag_lm_mtcars, type = "mf")
```

### Residuals vs fitted

```{r rf1}
plot(diag_lm_mtcars, type = "rf")
```

### Marginal-model plot

```{r mm1}
plot(diag_lm_mtcars, type = "mm", aes(x = hp))
```

### Added-variable plot

```{r av1}
plot(diag_lm_mtcars, type = "av", aes(x = hp))
```

### Component+Residuals plot

```{r cr1}
plot(diag_lm_mtcars, type = "cr", aes(x = hp))
```

## Example 2: lme

```{r example2}
library(nlme)
lme_od <- lme(distance ~ age + Sex, Orthodont, random = ~ 1 | Subject)
diag_lme_od <- diagnose(lme_od)
```

### Measured vs fitted

```{r mf2}
plot(diag_lme_od, type = "mf")
```

### Residuals vs fitted

```{r rf2}
plot(diag_lme_od, type = "rf")
```

### QQ norm

```{r qq2}
plot(diag_lme_od, type = "qq")
```

### QQ norm for random effects

```{r qq2r}
plot(diag_lme_od, type = "qq", aes(sample = .ranef.intercept), level = "Subject")
```

<!-- You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
-->
